Response to the defense feedback

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

To solve the problem, we use the debug information to split the bitmap into several segments and map the leakage site into the source code location. Each segment maps the address access situation of the function in the source code. In our setting, the max length of the bitmap of each segment is $1024$, the length of \textsf{uint1024\_t}. So we can put the bitmap into a variable. The split operation eases the computation. However, it also adds the limitation of the max address range when we quantify the side-channel leakage shown in Table~\ref{tab:size_limitation}. We think the range of the memory is big enough for us to quantify most of the cache side-channel attacks.

@@

\section{Implementation}
We have implemented a prototype of \ctool{}. It takes an input of ELF binary as well as the source code of the corresponding problem. The front-end of \ctool{} is implemented in Python. It can generate random inputs and test the program with these inputs many times.  The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input. The main component uses \textsf{libelfin}, an open-source library to parse ELF binaries and read DWARF debug information. The current implementation can support  64-bits ELF binary in Linux.

>>>>

To solve the problem, we use the debug information to split the bitmap into several segments and map the leakage site into the source code location. Each segment maps the address access situation of the function in the source code. In our setting, the maximal length of the bitmap of each segment is $1024$, the length of \textsf{uint1024\_t}. So we can put the bitmap into a variable. The split operation eases the computation. However, it also adds the limitation of the max address range when we quantify the side-channel leakage, as shown in Table~\ref{tab:size_limitation}. We believe the range of the memory is big enough for us to quantify most of the cache side-channel attacks.

@@

\section{Implementation}
We have implemented a prototype of \ctool{}. It takes an input of ELF binary as well as the source code of the corresponding program. The front-end of \ctool{} is implemented in Python. It can generate random inputs and test the program with these inputs many times.  The address record part is implemented as an Intel Pin tool plugin in C++ to record the bitmap for each input. The main component uses \textsf{libelfin}, an open-source library to parse ELF binaries and read DWARF debug information. The current implementation can support  64-bits ELF binary in Linux.
